This is an example of best mean and standard deviation using the Maximum-Likelihood Estimation, its based on:
https://www.r-bloggers.com/fitting-a-model-by-maximum-likelihood/

"It basically sets out to answer the question: what model parameters are most likely to characterise a given set of data? First you need to select a model for the data. And the model must have one or more (unknown) parameters. As the name implies, MLE proceeds to maximise a likelihood function, which in turn maximises the agreement between the model and the data."

```{r}
#Generating the data normally distributed
set.seed(1001)

N <- 100

x <- rnorm(N, mean = 3, sd = 2)

mean(x)
sd(x)



#Formulating the log-likelihood function

LL <- function(mu, sigma) {
     R = dnorm(x, mu, sigma)
     -sum(log(R))
 }

```

Okay, now the apply the MLE to estimate the mean and the standard deviation 

```{r}
library(stats4)


mle(LL, start = list(mu = 1, sigma=1))


```

Estimated coefficients are - mean = 3.012174, and std = 1.599490, what is pretty similar to the real ones

